Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-02 journal-draft/ettdoc_JG_section6.tex
update ettdoc_JG.tex with the changes from James.

\begin{mydef}
\label{def_centralized_clustering}
For a set of CR nodes $\mathcal{N}$, the \textbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where
\begin{enumerate}
\setlength{\itemindent}{.05in}
\item the intersection of any two clusters in $\mathcal{T}$ results in the empty set;
\item the union of all clusters in $\mathcal{T}$ results in$\mathcal{N}$;
\item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$;

\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$;
\item When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0, i.e. singleton clusters may be formed but do mot contribute to the objective function.
In particular, the range can be expressed as $[\delta-u, \delta+u]$, where $\delta$ is the desired cluster size, $u$ is a constant and $\delta-u > 0$.

\end{enumerate}
\end{mydef}
% XXX Di: What does the last statement mean with respect to the size of C being allowed to be 1. Does that mean for all C in T, the size is allowed to be 1? Doesn't that contradict what you have been saying in the definition before, where you come up with the range ?
% XXXX 
%1. we have a function f(C) to denote the number of CCs, if cluster size is in the scope, fine; if not, f(C) equals zero.
%2. it is OK for every CR node to form their own cluster. Then according to rule 3, f(C) is zero and we obtain a 'bad' clustering result.
% XXXX

@@

\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$N$ is the total number of CR users in network $\mathcal{N}$.
$y_i$ and $x_{ij}$ are two binary variables.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$.

@@

%The optimization is a binary linear programming problem.
As to the objective function, the sum of the first items is the sum of CCs of the clusters which constitute the CRN.
In the second item, we propose $p(C_i)$ which is a size-related weight for cluster $C_i, i\in{1,\cdots, M}$.
$p(C_i)$ is positively related with the difference between $C_i$'s size and the desired size $\delta$.
The desired size $\delta$ is pre-decided based on the capability of the CR users and the tasks to be conveyed.
When $y_i$ is 1 ($C_i$ is chosen) but $|C_i|$ doesn't equal to the desired cluster size $\delta$, it will be negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
The weight $p(C_i)$ with respect to different cluster sizes is as follows,
%$$
%p(C_i) = \left\{ \begin{array}{rl}
%0 &\mbox{ if $|C_i|=\delta$} \\
%\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
%\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
%\vdots\\
%\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
%\end{array} \right.
%$$

$$
p(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho_1 &\mbox{if $|C_i|=\delta \pm 1$ } \\
\rho_2 &\mbox{if $|C_i|=\delta \pm 2$} \\
\vdots\\
\rho_\sigma &\mbox{if $|C_i|=\delta \pm \sigma$} \\
\end{array} \right.
$$
where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.
Please note that here we adopt the desired cluster size in stead of the range for cluster sizes which is described in Definition~\ref{problem}.
Because in implementation, we usually need a large range to guarantee a feasible result for the optimization problem.
By adopting the desired size and the punishment for deviating from it, we actually set a large range of cluster sizes and meanwhile a better control of the resulted sizes.

@@

In this section we introduce our distributed clustering schemes.
With the variants of ROSS, CR nodes form clusters based on their own available channels, as well as the available channels of the nodes in their neighborhood.
This clarified and conducted through a series of interactions on the control channel.
All variants of ROSS consist of two cascaded phases: \textit{Cluster formation} and \textit{Membership clarification}, as shown in Figure~\ref{flowChartROSS}.
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.9\linewidth]{flow_chart.pdf}
	\caption{Processing steps of ROSS}
	\label{flowChartROSS}
\end{figure}
In the first phase, clusters are initially formed such that every CR user becomes either cluster head or cluster member.
During this phase, size control is already realized, however, memberships might not be efficient with respect to robustness while also not being necessarily unique.
This is addressed in the second phase, where non-overlapping clusters are formed in a way that the CCs of the involved clusters are predominantly increased.

\subsection{Phase I - Cluster Formation}
\label{phaseI}
Before conducting clustering, we assume spectrum sensing and neighborhood discovery have been completed.
Furthermore, neighboring nodes have exchanged already their channel availabilities via the dedicated control channel. 
As a result, every CR node is aware of the available channels of themselves and their one-hop neighbors.
Next, cluster heads are determined after a comparison series among neighbors.
Two metrics are proposed to characterize the channel availability in the proximity of each terminal, which subsequently are used to decide the cluster heads.
\begin{itemize}

\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
$d_i$ is the total number of the CCs between node $i$ and each of its neighbors, it does not reflect the amount of jointly common channels among all neighbors of $i$.
\item \textit{Neighborhood connectivity degree} $g_i$: In contrast, $g_i$ is the number of CCs which are available for $i$ and all of its neighbors, thus
$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It therefore represents the ability of $i$ to form a robust cluster with its neighbors.
\end{itemize}
Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector} $(d_i, g_i)$.
The connectivity vector is determined by every secondary user and is then broadcasted.
Figure~\ref{fig1} illustrates the computation of the connectivity vectors for a CRN, where dashed edges indicate that the nodes are within each other's transmission range, while the number along the dashed line is the number of common channels between the two ends.
In this example, the set of available channels per terminals are given by: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$. 
The figure shows in particular the resulting connectivity vector per node.
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Illustration of the resulting connectivity vector $(d_i, g_i)$ for each node of an example CRN.}
	\label{fig1}
\end{figure}

@@

To control the cluster size, cluster heads remove their cluster members when cluster sizes are larger than a threshold.
The threshold should be larger than the desired size $\delta$, because there are overlaps between neighboring clusters.
%Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
We set the threshold as $t\cdot \delta$, where the constant parameter $t$ is dependent on the network density and CR nodes' transmission range.
We adopt $t$ to be between 1 and the ratio of the average neighborhood size and desired size.
When $t$ is smaller, \eg $t=1$, the formed cluster in phase I will be $\delta$.
For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the following membership clarification phase.
If $t$ is chosen large, \eg $t\cdot\delta$ equals the size of the neighborhood, the mechanism of adjusting the cluster size will not work any more.

@@

\subsubsection{Distributed Greedy Algorithm (DGA)}
When a debatable node $i$ decides to join cluster $C\in S_i$, the guiding idea is that its decision should result in the greatest increase of CCs in all its claiming clusters.
As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will result in a claiming cluster if $i$ leaves that cluster.
Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in a lower increase in terms of CCs than leaving any other claiming clusters in $S_i$.
%As to a cluster $C\in S_i$, if $i$ leaves cluster $C$ and results in less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
In case of a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
When a tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
Node IDs of cluster heads will be used to break tie in the end if necessary.
The pseudo code of this algorithm is given by Algorithm~\ref{alg4}.
After deciding its membership, debatable node $i$ notifies all its claiming clusters.
%xxxxxxxxxxxxxxxxxxx

@@

To formulate the debatable nodes' membership clarification into a congestion game, we reexamine this process from a different perspective. 
Thus, debatable nodes are not included in any cluster and they need to decide on one cluster to join.
When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.37\linewidth]{singletongame_matching.pdf}
  \caption{Illustration of debatable nodes and claiming clusters}
  \label{debatable_nodes_claiming_cluster}
\end{figure}

In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$ with the following elements:

@@

Alternatively, we can consider the total share of users (still) residing in a cluster after the addition of the primary users as performance metric for robustness.
If we do so, the ROSS-based schemes maintain 5\%, 30\% and 230\% more secondary users within clusters than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively (no figure is provided for this data).
%XXXXX
The above observation illustrates clearly that the average number of CCs of non-singleton clusters doesn't necessarily reflect the robustness of clusters, \ie SOC obtains the most CCs among the distributed schemes, but the resulting clusters are vulnerable to primary user activity.

We finally turn to a comparison of the involved signaling overhead for the different clustering schemes.
For this, we count the number of \textit{transmissions of control messages} as metric~\cite{complexity_aggregation_2011}, without distinguishing broadcast or uni-cast control messages.
%In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
%We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
%According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.

As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
The upper limits for the message exchanges are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA, respectively.
SOC consists of three rounds, and in each round every node needs to perform a broadcast to do comparisons and cluster merging.
The centralized scheme is conducted at some control device, which involves information aggregation and subsequent dissemination of clustering decisions.
To analyze the centralized scheme's message overhead, we adopt a backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc}, and apply ROSS to generate cluster heads which serve as the backbone.
In the stage of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller. 
In the dissemination stage, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper limit for the number of broadcast is $N+m+n$.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.6\linewidth]{number_controlMsg.pdf}
  \caption{Absolute amount of control messages required for clustering.}
%XXXXXX Quantitative, or Absolute
  \label{control_msg}
\end{figure}

\subsection{Comparison among the Distributed Schemes}
\label{largeScaleCRN}
We now switch to a more fine-grained investigation only of the distributed schemes. 
We are here most important interested in their properties when the network size and density scales.
In our scenario, we set now the transmission range of CR to $A/5$ while the primary user transmission range is set to $2A/5$.
The initial number of primary users is set to 30.
%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
As we scale now the number CR nodes in the scenario, we adjust the desired size in the clustering process.
Our adopted values are listed in the Table~\ref{Simulation_para}, which represent about 60\% of the average number of neighbors.
%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.

\begin{table}[ht]
\caption{}
\label{Simulation_para}
{\small
%\hfill{}
\begin{tabular}{|L{3 cm}|C{0.85 cm}|C{0.85 cm}|C{0.85 cm}|}
\hline
Number of CRs			& 100 	&  200 					& 300 \\ \hline
Average num. of neighbors 	&9.5	&   20		& 31  \\ \hline
Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
\end{tabular}
}
%\hfill{}
\end{table}

\subsubsection{Number of CCs per Non-singleton Clusters}

>>>>

\begin{mydef}
\label{def_centralized_clustering}
For a set of CR nodes $\mathcal{N}$, the \texbf{CRN robust clustering problem} is to determine a set of clusters $\mathcal{T}$, where 
\begin{enumerate}
\setlength{\itemindent}{.05in}
\item the intersection of any two clusters in $\mathcal{T}$ results in the empty set;
\item the union of all clusters in $\mathcal{T}$ results in$\mathcal{N}$;
\item the sum over $f(C)$ for all clusters $C$ is maximized, where the number of common channels for cluster $C$ is denoted as $f(C)$;

\item all cluster sizes are within the range $\big[\delta_1, \delta_2\big]$, with $\delta_1, \delta_2\in \mathbb{Z}^+$ and $\delta_1 \leq \delta_2$;
\item When the cluster size is larger or smaller than the range $\big[\delta_1, \delta_2\big]$, $f(C)$ is defined as 0, i.e. singleton clusters may be formed but do mot contribute to the objective function.

\end{enumerate}
\end{mydef}

@@

\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot t_{ij}) \\
     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, for\,\,\forall j=1, \ldots, N \\
   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, for\,\,\forall i=1, \ldots, M \\
  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$y_i$ and $x_{ij}$ are two binary variables.
% where $j\in \{1,2,\cdots,N-1, N\}$ and $i\in \{1,2,\cdots,M-1, M\}$.
%$G = |\mathcal{G}|$ and there is $\mathcal{G} \subseteq \mathcal{S}$.
Being either 1 or 0, $y_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$x_{ij}$ indicates whether the CR node $j$ resides in the cluster $C_i$, \ie $x_{ij}=1$ means node $j$ resides in the cluster $C_i$. 
%Node index $j$ is identical to the node ID.
$N$ is the total number of CR users in network $\mathcal{N}$, $M$ is the number of clusters in $\mathcal{S}$.

@@

%The optimization is a binary linear programming problem.
The objective is to maximize the sum of the numbers of CCs in the clusters which constitute the CRN.
$t_{ij}$ is a constant and there is
%In practice, we can solve the problem with $\mathcal{G} = \mathcal{S}$ when $|\mathcal{S}|$ is not large. 
%
%
%Given a CRN $\mathcal{N}$ and desired cluster size $\delta$, we obtain a collection of clusters $\mathcal{G}$ which contains all the \textit{potential} clusters, and the sizes of these clusters are $1,2,\ldots,\delta$.
%Potential clusters are the clusters which satisfy the conditions introduced in Section~\ref{sec:model}. 
%Note that the potential clusters include the singleton ones.
%By permitting the existence of the singleton clusters, we can ensure that the $\mathcal{S}'$ in Definition~\ref{def_centralized_clustering} is always be feasible.

\begin{equation}
t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
\end{equation}
where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
$p(C_i)$ is the size-related weight, which is positively related with the difference between $C_i$'s size and the desired size $\delta$.
The desired size $\delta$ is decided based on the capability of the CR users and the tasks to be conveyed.
The weight $p$ is decided with respect to cluster sizes 1,2, $\cdots$, $\sigma$ as follows,
$$
p(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
\vdots\\
\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
\end{array} \right.
$$
where $ 0 < \rho_1< \rho_2 < \cdots < \rho_\sigma$.

%%Based on the knowledge on $\mathcal{S}$, we construct a $M\times N$ matrix $Q_{M\text{x}N}$ which is shown in Figure~\ref{costant_matrix_Q}. 
%%Constant $q_{ij}$ is the element of $Q_{M\text{x}N}$, and its subscripts correspond to the $i$th cluster and CR node $j$ respectively.
%$q_{ij}= |K(C_i)|/|C_i|$ when there is $j\in C_i$, and $q_{ij}= 0$ when there is $j\notin C_i$.
%In other words, each non-zero element $q_{ij}$ means the number of CCs of the cluster $i$ where node $j$ resides.

%\begin{figure}[ht!]
%\centering
%\bordermatrix{~ 		& 1 	& 2 	& 3 	& \cdots & j & \cdots	& N-1 	& N	\cr
%                  1 	& |K(C_1)| 	& |K(C_1)| 	& 0 	& \cdots & \cdots &\cdots	& 0 	& 0	\cr
%                  2 	& |K(C_2)| 	& 0 	& |K(C_2)| 	& \cdots & \cdots & \cdots 	& 0 	& 0	\cr
%				\vdots  	&\vdots & 	 	& 		&  \vdots		& 		& \vdots \cr
%				i 	& 0 	& |K(C_i)| 	& 0 	& \cdots  & \cdots & \cdots 	& |K(C_i)| 	& 0	\cr
%				\vdots  	&\vdots & 	 	& 		&  \vdots & \cdots & \vdots 		& 		& \vdots \cr
%				\vdots 	& 0  	& 0 	& 0 	& \cdots & \cdots & \cdots 	& |K(C_i')| 	& 0	\cr
%				G  	& |K(C_G)| & \cdots	 	& 		&  \vdots	& \cdots & \vdots& 		& \vdots \cr}	
%\caption{An example of Matrix $Q$, its rows correspond to all possible clusters, and columns correspond to the CR nodes in the CRN. }
%\label{costant_matrix_Q}
%\end{figure}

%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p(C_i)$, the objective function becomes,
\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
The sum of the first items is the sum of CCs of all the chosen clusters.
As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.

@@

In this section we introduce our distributed clustering schemes.
With the variants of ROSS, CR nodes form clusters based on their own available channels, as well as the available channels of the nodes in their neighborhood.
This clarified and conducted through a series of interactions on the control channel.
All variants of ROSS consist of two cascaded phases: \textit{Cluster formation} and \textit{membership clarification}, as shown in Figure~\ref{flowChartROSS}.
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.9\linewidth]{flow_chart.pdf}
	\caption{Processing steps of ROSS}
	\label{flowChartROSS}
\end{figure}
In the first phase, clusters are initially formed such that every CR user becomes either cluster head or cluster member.
During this phase, size control is already realized, however, memberships might not be efficient with respect to robustness while also not being necessarily unique.
This is addressed in the second phase, where non-overlapping clusters are formed in a way that the CCs of the involved clusters are predominantly increased.

\subsection{Phase I - Cluster Formation}
\label{phaseI}
Before conducting clustering, we assume spectrum sensing and neighborhood discovery have been completed.
Furthermore, neighboring nodes have exchanged already their channel availabilities via the dedicated control channel. 
As a result, every CR node is aware of the available channels of themselves and their one-hop neighbors.
Next, cluster heads are determined after a comparison series among neighbors.
Two metrics are proposed to characterize the channel availability in the proximity of each terminal, which subsequently are used to decide the cluster heads.
\begin{itemize}
\item \textit{Individual connectivity degree} $d_i$: $d_i=\sum_{j\in \text{Nb}(i)}\vert K_i\cap K_j\vert$. 
$d_i$ is the total number of the CCs between node $i$ and each of its neighbors, it does not reflect the amount of jointly common channels among all neighbors of $i$.
\item \textit{Neighborhood connectivity degree} $g_i$: In contrast, $g_i$ is the number of CCs which are available for $i$ and all of its neighbors, thus
$g_i=|\bigcap_{j\in \text{Nb}(i)\cup i}K_j|$. It therefore represents the ability of $i$ to form a robust cluster with its neighbors.
\end{itemize}
Individual connectivity degree $d_i$ and neighborhood connectivity degree $g_i$ together form the \textit{connectivity vector} $(d_i, g_i)$.
The connectivity vector is determined by every secondary user and is then broadcasted.
Figure~\ref{fig1} illustrates the computation of the connectivity vectors for a CRN, where dashed edges indicate that the nodes are within each other's transmission range, while the number along the dashed line is the number of common channels between the two ends.
In this example, the set of available channels per terminals are given by: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, \\K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, \\K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, \\K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$. 
The figure shows in particular the resulting connectivity vector per node.
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Illustration of the resulting connectivity vector $(d_i, g_i)$ for each node of an example CRN.}
	\label{fig1}
\end{figure}

@@

To control the cluster size, cluster heads remove their cluster members when cluster sizes are larger than a threshold.
The threshold should be larger than the desired size $\delta_1$, because there are overlaps between neighboring clusters.
%Hence, a cluster head excludes some cluster members when the cluster size exceeds a certain threshold.
We set the threshold as $t\cdot \delta$, where the constant parameter $t$ is dependent on the network density and CR nodes' transmission range.
We adopt $t$ to be between 1 and the ratio of the average neighborhood size and desired size.
When $t$ is smaller, \eg $t=1$, the formed cluster in phase I will be $\delta$.
For the cluster whose members are included by other clusters, the size of this cluster will be smaller than $\delta$ after the following membership clarification phase.
If $t$ is chosen large, \eg $t\cdot\delta$ equals the size of the neighborhood, the mechanism of adjusting the cluster size will not work any more.

@@

\subsubsection{Distributed Greedy Algorithm (DGA)}
When a debatable node $i$ decides to join cluster $C\in S_i$, the guiding idea is that its decision should result in the greatest increase of CCs in all its claiming clusters.
As node $i$ has been notified of the spectrum availability on all the nodes in each claiming cluster, node $i$ is able to calculate how many more CCs will result in a claiming cluster if $i$ leaves that cluster.
Then node $i$ decides on the cluster $C\in S_i$, if $i$ leaving cluster $C$ results in a lower increase in terms of CCs than leaving any other claiming clusters in $S_i$.
%As to a cluster $C\in S_i$, if $i$ leaves cluster $C$ and results in less increased CCs than leaving any other claiming clusters, then $i$ chooses to stay in cluster $C$.
In case of a tie between two claiming clusters, $i$ chooses to stay in the cluster whose cluster head shares the most CCs with $i$.
When a tie still exists, node $i$ chooses to stay in the claiming cluster which has the smallest size.
Node IDs of cluster heads will be used to break tie in the end if necessary.
The pseudo code of this algorithm is given by Algorithm~\ref{alg4}.
After deciding its membership, debatable node $i$ notifies all its claiming clusters.

@@

To formulate the debatable nodes' membership clarification into a congestion game, we reexamine this process from a different perspective. 
Thus, debatable nodes are not included in any cluster and they need to decide on one cluster to join.
When a debatable node $i$ joins one cluster $C$, the decrease of CCs in cluster $C$ is $\sum_{C\in S_i}\Delta\vert K(C) \vert=\sum_{C\in S_i}({\vert K(C) \vert-\vert K(C\cup i) \vert})$.
Then, node $i$ chooses the cluster $C$, where the decrease of CCs in cluster $C$ is smaller than the decrease if $i$ would have joined any other claiming cluster in $S_i$.
The relation between the debatable nodes and the claiming clusters is shown in Figure~\ref{debatable_nodes_claiming_cluster}.
\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.37\linewidth]{singletongame_matching.pdf}
  \caption{Illustration of debatable nodes and claiming clusters}
  \label{debatable_nodes_claiming_cluster}
\end{figure}
In the following, we show that the decision of debatable nodes to clarify their membership can be mapped to the behaviour of the players in a \textit{player-specific singleton congestion game} when proper cost function is given.
The game to be constructed is represented with a 4-tuple $\Gamma=(\mathcal{P},\mathcal{R},\sum_{i, i \in \mathcal{P}}, f)$ with the following elements:

@@

Alternatively, we can consider the total share of users (still) residing in a cluster after the addition of the primary users as performance metric for robustness.
If we do so, the ROSS-based schemes maintain 5\%, 30\% and 230\% more secondary users within clusters than SOC, when the numbers of newly added PR are 10, 40 and 80 respectively (no figure is provided for this data).
The above observation illustrates clearly that the average number of CCs of non-singleton clusters doesn't necessarily reflect the robustness of clusters, \ie SOC obtains the most CCs among the distributed schemes, but the resulting clusters are vulnerable to primary user activity.

We finally turn to a comparison of the involved signaling overhead for the different clustering schemes.
For this, we count the number of \textit{transmissions of control messages} as metric~\cite{complexity_aggregation_2011}, without distinguishing broadcast or uni-cast control messages.
%In Section~\ref{ross}, this metric is synonymous with the \textit{the number of updates}.
%We don't consider the the control messages which are involved in neighborhood discovery, which is the premise and deemed to be the same for all clustering schemes.
%According to~\cite{complexity_aggregation_2011}, the message complexity is defined as the number of messages used by all nodes.
As to ROSS, in the first phase the maximal number of broadcast is $N$ according to~\ref{clustering:theorem}.
The upper limits for the message exchanges are $n^2m$ and $n$ for ROSS-DGA and ROSS-DFA, respectively.
SOC consists of three rounds, and in each round every node needs to perform a broadcast to do comparisons and cluster merging.
The centralized scheme is conducted at some control device, which involves information aggregation and subsequent dissemination of clustering decisions.
To analyze the centralized scheme's message overhead, we adopt a backbone structure proposed in~\cite{Efficient_broadcasting_gathering_adhoc}, and apply ROSS to generate cluster heads which serve as the backbone.
In the stage of information aggregation, all the nodes transmit information to the cluster heads which forward the messages to the controller. 
In the dissemination stage, all the cluster heads and the debatable nodes broadcast the clustering result, thus the upper limit for the number of broadcast is $N+m+n$.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.6\linewidth]{number_controlMsg.pdf}
  \caption{Absolute amount of control messages required for clustering.}
  \label{control_msg}
\end{figure}

\subsection{Comparison among the Distributed Schemes}
\label{largeScaleCRN}
We now switch to a more fine-grained investigation only of the distributed schemes. 
We are here most important interested in their properties when the network size and density scales.
In our scenario, we set now the transmission range of CR to $A/5$ while the primary user transmission range is set to $2A/5$.
The initial number of primary users is set to 30.
%The number of CR is 100, 200 and 300, and the average number of neighbours of each CR is 9.5, 20, and 31.
As we scale now the number CR nodes in the scenario, we adjust the desired size in the clustering process.
Our adopted values are listed in the Table~\ref{Simulation_para}, which represent about 60\% of the average number of neighbors.
%When run ROSS, the parameter $t$ which is used to control cluster size in phase I is 1.3.
\begin{table}[ht]
\caption{}
\label{Simulation_para}
{\small
%\hfill{}
\begin{tabular}{|L{3 cm}|C{0.85 cm}|C{0.85 cm}|C{0.85 cm}|}
\hline
Number of CRs			& 100 	&  200 					& 300 \\ \hline
Average num. of neighbors 	&9.5	&   20		& 31  \\ \hline
Desired size $\delta$ 	& 6	&   12 						& 20      \\ \hline
\end{tabular}
}
%\hfill{}
\end{table}
